Does freshwater connectivity influence phosphorus retention in lakes?

### 2019-01-23 manuscript/manuscript.Rmd
update tables to accepted formatting

Differences in P retention among lakes with different connectivity metric values was reflected in differences among connectivity class-specific values of the P decay parameter $k$ (Figure 7). The connectivity metric that had the most effect on $k$ was average link length (Table 2). For instance, hierarchical models fit with the average link length metric had a median effect size of 0.23 and 0.05 for $k$ and P retention respectively (Table \ref{table2}{2}), which means that for this metric, lakes with shorter average link lengths retained 4.7 to 4.9\% more P than lakes with longer average link lengths. The influence of lake-stream-based connectivity metrics on lake P retention was similar to stream-based connectivity metrics (Figure 7). This suggests that both lake-stream-based connectivity between lakes and streams as well as stream-based connectivity of lakes and their terrestrial watersheds influence P retention (Figure \ref{fig2}).

\begin{figure*} \ContinuedFloat
  \begin{center}
    \includegraphics[width=0.85\textwidth,keepaspectratio]{../tables/crop/02_model_results_table} 
    \captionsetup{labelformat=empty}
    \caption{\textbf{Table 2. } Connectivity class split values and samples sizes for connectivity metrics and lake depth ranked according to the difference in median $k$ (P decay parameter, $\Delta$k) values. Differences in $\Delta$k that translate to differences in P retention greater than measurement precision are marked with an asterisk. Here, WS is the lake watershed extent whereas SWS is the lake subwatershed extent. Lakes with metric values above or equal to the split value were assigned to a separate connectivity class relative to lakes below the split value. N is sample size. Connectivity metrics are defined in Figure 2.}\label{table2}    
  \end{center}
\end{figure*}

>>>>

Differences in P retention among lakes with different connectivity metric values was reflected in differences among connectivity class-specific values of the P decay parameter $k$ (Figure 7). The connectivity metric that had the most effect on $k$ was average link length (Table 2). For instance, hierarchical models fit with the average link length metric had a median effect size of 0.23 and 0.05 for $k$ and P retention respectively (Table \ref{table2}), which means that for this metric, lakes with shorter average link lengths retained 4.7 to 4.9\% more P than lakes with longer average link lengths. The influence of lake-stream-based connectivity metrics on lake P retention was similar to stream-based connectivity metrics (Figure 7). This suggests that both lake-stream-based connectivity between lakes and streams as well as stream-based connectivity of lakes and their terrestrial watersheds influence P retention (Figure \ref{fig2}).

\begin{figure*} \ContinuedFloat
  \begin{center}
    \includegraphics[width=0.85\textwidth,keepaspectratio]{../tables/crop/02_model_results_table} 
    \captionsetup{labelformat=empty}
    \caption{\textbf{Table 2. } Connectivity class split values and samples sizes for connectivity metrics and lake depth ranked according to the difference in median $k$ (P decay parameter, $\Delta$k) values. Differences in $\Delta$k that translate to differences in P retention greater than measurement precision are marked with an asterisk. Here, WS is the lake watershed extent whereas SWS is the lake subwatershed extent. Lakes with metric values above or equal to the split value were assigned to a separate connectivity class relative to lakes below the split value. N is sample size. Connectivity metrics are defined in Figure \ref{fig2}.}\customlabel{table2}{2}    
  \end{center}
\end{figure*}
